When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-15 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
added protocol registration section

@@

>>>>

## Protocol registration

The Stage 1 Registered Report protocol has been approved and is available at [osf.io/qa2bg/](https://osf.io/qa2bg/).

@@

## Manipulation checks

The performance measure *d’* did not change across *n*-back levels (`r apa_print(hypothesis1a_rmanova)$full_result$level`), but the median RT did (`r apa_print(hypothesis1b_rmanova)$full_result$level`).
Specifically, the median RT was higher for the more difficult level in every contrast, with two exceptions:
The median RT did not differ between 2-back and 4-back, and the median RT was higher for 3-back than for 4-back (Table\ \@ref(tab:H1b-contrasts)).

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts,
  caption = "Paired contrasts for the rmANOVA comparing the median reaction time between *n*-back levels",
  note = "The column Contrast contains the $n$ of the *n*-back levels. $SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.",
  escape = FALSE,
  placement = "H"
)
```

## Decline of subjective values

## Differences between NFC groups
